---
title: "Hello, Stress & Development Lab!"
author: "John Flournoy"
date: "1/11/2018"
output: 
  ioslides_presentation:
    incremental: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, error = FALSE, message = FALSE)
```

## Introduction

My work in graduate school has been diverse

- Social 
- Neuroscience
- Development
- Personality

## Interests

My interests are both

- Substantive
    - Adolescent, motivated decision-making
    - Development of stable individual differences
- Methodological
    - Cognitive models of behavior
    - Refined models of development
    - Emphasis on uncertainty

## Projects

Four projects (and what I've learned about doing science from some of them):

1. Neural correlates of empathy-motivated prosocial behavior
2. Interactions between personality and values in adult development
3. The Yellow Light Game and adolescent risk-taking
4. Measuring adolescent-developing motivations

# Neural correlates of empathy-motivated prosocial behavior

Do individual differences in empathic concern predict future prosocial behavior? Is this mediated by "affective resonance" neural processes?

## Empathy and Prosocial Behavior

*Empathic concern:* Sympathy, compassion; aligned emotions _for_ another person's suffering. 

Evidence of association between EC and prosocial behavior throughout development (Barr & Higgins-D’Alessandro, 2007; Brownell et 
al., 2013; Eisenberg, 2003; Eisenberg et al., 1991; Eisenberg et al., 1987; Farrant et
al., 2012; 
Litvack-Miller et al., 1997)

## What reactive neural processes are involved?

Empathic concern is an emotional reaction that will be activated by other people's emotional expressions.

Given that a neural region is functionally active in response to other people's emotions, does that functional activation explain some of the link between EC and prosocial behavior?

What does a particular region's involvement tell us about this link?

## The study

Two waves, only participants with fMRI at wave 1 & 2.

>- $N = 56 (N_{\text{male}} = 26$)
>- fMRI during passive viewing of emotional faces (NimStim).
>- Questionnaires

## Measures

Measures of target constructs:

- Interpersonal Reactivity Index (cite)
    - Empathic Concern
    - Personal Distress
- Questions from the 4-H Study of Positive Youth Development survey (Lerner et al., 2005)
    - >During an average week, how many 
hours do you spend helping other people without getting paid (such as helping out at a hospital, 
daycare center, food shelf, youth program, community service agency, or doing other things)
    - Item asking if they are often kind to other children.

## Descriptives at a glance

```{r}
library(tidyverse)
knitr::kable(
    tribble(
        ~Wave, ~`Age Mean`, ~`(SD)`,
        1, 10.1, '(.31)',
        2, 13.1, '(.31)'
        
    )
)
```
